Racial and Ethnic Differences in ETI

### 2024-01-03 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti.qmd
Update racial_and_ethnic_differences_in_eti.qmd

---
title: "Racial and Ethnic Differences in ETI"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    number-sections: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Users/timvigers/Dropbox/Miscellaneous/zotero.bib
csl: /Users/timvigers/Dropbox/Miscellaneous/american-medical-association.csl
editor: source
---

@@

```{r}
# Calculate time from first ETI use
encounter <- encounter %>%
  mutate(
    days_from_start =
      as.numeric(encounterdate - Modulator_trikafta_first_date)
  )
# Segmented regression by group
lm_fixed_cp <- segreg(
  GLI_FEV1_pct_predicted ~ race + seg(days_from_start, by = race),
  data = encounter
)
# Results
lm_fixed_cp$psi
slope(lm_fixed_cp)
# Plot
new_df = lm_fixed_cp$model
new_df$pred = predict(lm_fixed_cp)
ggplot(new_df, aes(x = days_from_start, y = pred,group = race,color = race)) +
  geom_line() +
  ylim(0, 150)
# # Random intercept version isn't converging
# # Basic model
# lmm_base <- lme(GLI_FEV1_pct_predicted ~ days_from_start,
#   random = ~ 1 | eDWID, data = encounter, na.action = na.omit,method = "ML",
#   control=list(msMaxIter=1000,msMaxEval = 1000)
# )
# # Segmented with fixed change point
# lmm_fixed_cp <- segmented(lmm_base,
#   seg.Z = ~days_from_start, psi = 0,
#   random = list(eDWID = pdDiag(~ 1 + days_from_start + U))
# )
```

```{r}
#| cache: true
#| eval: false
t <- encounter %>%
  select(eDWID, GLI_FEV1_pct_predicted, days_from_start) %>%
  drop_na()

model <- list(
  GLI_FEV1_pct_predicted ~ 0 + days_from_start,
  ~ 0 + days_from_start
)
fit <- mcp(model, data = t, cores = 4, chains = 4)
plot(fit)
```

>>>>

---
title: "Racial and Ethnic Differences in ETI"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    number-sections: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: C:/Users/timvigers/Dropbox/Miscellaneous/zotero.bib
csl: C:/Users/timvigers/Dropbox/Miscellaneous/american-medical-association.csl
editor: source
---

@@

```{r}
# Calculate time from first ETI use
encounter <- encounter %>%
  mutate(
    days_from_start =
      as.numeric(encounterdate - Modulator_trikafta_first_date)
  )
# Segmented regression by group
lm_fixed_cp <- segreg(
  GLI_FEV1_pct_predicted ~ race + seg(days_from_start, by = race),
  data = encounter
)
# Results
lm_fixed_cp$psi
slope(lm_fixed_cp)
# Plot
new_df = lm_fixed_cp$model
new_df$pred = predict(lm_fixed_cp)
ggplot(new_df, aes(x = days_from_start, y = pred,group = race,color = race)) +
  geom_line() +
  ylim(0, 150)
# # Random intercept model isn't converging
# # Basic model
# lmm_base <- lme(GLI_FEV1_pct_predicted ~ days_from_start,
#   random = ~ 1 | eDWID, data = encounter, na.action = na.omit,method = "ML",
#   control=list(msMaxIter=1000,msMaxEval = 1000)
# )
# # Segmented with fixed change point
# lmm_fixed_cp <- segmented(lmm_base,
#   seg.Z = ~days_from_start, psi = 0,
#   random = list(eDWID = pdDiag(~ 1 + days_from_start + U))
# )
```

```{r}
#| cache: true
t <- encounter %>%
  select(eDWID, GLI_FEV1_pct_predicted, days_from_start) %>%
  drop_na()
model <- list(
  GLI_FEV1_pct_predicted ~ 0 + days_from_start,
  ~ 0 + days_from_start
)
fit <- mcp(model, data = t, cores = 4, chains = 4)
plot(fit)
```
